---
title: 'DTSC 550: Intro to Statistical Modeling'
subtitle: 'CG Lab 1 Template'
output: html_notebook
editor_options:
  chunk_output_type: inline
---

# Student Info

*Name:* Ryan Dotson

*Term:* Spring 1 2026

*Date:* 01-15-2026


# Questions

## Question 1 (aka, Q1): Create a variable called Q1 containing the names of my family: "Jeff", "Emily", and "Isabella".

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q1 #

### TYPE YOUR CODE BELOW ###

Q1 <- c('Jeff', 'Emily', 'Isabella')

### Viewing your variable is an important habit to get into. This helps you ensure your output is as expected. 
Q1
```

## Q2: Create a variable called `eicher_height` containing the value of 5.833. Convert `eicher_height` from feet to centimeters and assign the result to Q2. Do not round.

*Note: If you don't know how to convert feet to centimeters, find the conversion factor on Google. Do not install a package or use a special function; CodeGrade is not set up to accept that approach.*

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q2 #

### TYPE YOUR CODE BELOW ###

eicher_height <- 5.833
Q2 <- eicher_height * 30.48

### VIEW OUTPUT ###
Q2

```

## Q3: Create a variable called `my_fam_heights` with a vector containing the values 5.833, 5.6, and 2.1. Get the 2nd element by indexing the `my_fam_heights` variable. Assign it to Q3.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q3 #

###TYPE YOUR CODE BELOW###

my_fam_heights <- c(5.833, 5.6, 2.1)
Q3 <- my_fam_heights[2]

#### VIEW OUTPUT ###
Q3

```

## Q4: Create a copy of my_fam_heights, called `new_fam_heights`. Change the 3rd value to 2.2 and store new_fam_heights as Q4.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q4 #

### TYPE YOUR CODE BELOW ###

new_fam_heights <- my_fam_heights
new_fam_heights[3] <- 2.2
Q4 <- new_fam_heights

### VIEW OUTPUT ###
Q4

```

## Q5: Create Q5 with the mean (i.e. average) of Q4.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q5 #

### TYPE YOUR CODE BELOW ###

Q5 <- mean(Q4)

### VIEW OUTPUT ###
Q5

```

## Q6: Round Q5 to one decimal place and assign the result to Q6.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q6 #

### TYPE YOUR CODE BELOW ###

Q6 <- round(Q5, 1)

### VIEW OUTPUT ###
Q6

```

## Q7: Find the median of Q4 and assign the result to Q7.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q7 #

### TYPE YOUR CODE BELOW ###

Q7 <- median(Q4)

### VIEW OUTPUT ###
Q7

```

## Q8: Convert all the heights stored in Q4 (as feet) to centimeters and assign the result to Q8.

```{r}
### Do not change and do not delete the comment below. It is required for Code Grade to run properly.
# CG Q8 #

### TYPE YOUR CODE BELOW ###

Q8 <- Q4 * 30.48

### VIEW OUTPUT ###
Q8

```
