---
title: 'DTSC 550: Intro to Statistical Modeling'
subtitle: 'CG Lab 2 Template'
output: html_notebook
editor_options:
  chunk_output_type: inline
---

# Student Info

*Name:* Ryan Dotson

*Term:* Spring 1 2026

*Date:* 01-15-2026


# Questions

## Part 1

The dataframe is called *`usairports`* within the airports package. Let's view the dataframe by running the following code block. Take some time to familiarize yourself with the columns and rows.

```{r}
usairports
```

### Q1: View the data in only the first 4 rows of the usairports dataframe. Store this result to a variable called Q1.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
## CG Q1 ##

### TYPE YOUR CODE BELOW ###

Q1 <- head(usairports, 4)

### VIEW OUTPUT ###
Q1

```

### Q2: Assign the dimensions of the usairports dataset to a variable called Q2.

Do not hard code the answer! That is, do not simply have `Q2 <- {a number}`

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q2 #

### TYPE YOUR CODE BELOW ###

Q2 <- dim(usairports)

### VIEW OUTPUT ###
Q2

```

### Q3: Store the last 5 rows of the usairports dataframe and view only columns 5, 6, & 7. Use indexing to access the requested columns. Store this result to a variable called Q3.

For assistance with indexing, refer to this [article](https://www.geeksforgeeks.org/how-to-select-dataframe-columns-by-index-in-r/). Be careful, though, not to use the last approach, which utilizes the dplyr library. This lab does not allow the use of dplyr functions.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q3 #

### TYPE YOUR CODE BELOW ###

Q3 <- tail(usairports, 5)[, c(5:7)]

### VIEW OUTPUT ###
Q3

```

### Q4: Store the names of the first six variables in the usairports dataframe to Q4.

Do not hard code the answer! That is, do not simply type the names of the columns.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q4 #

### TYPE YOUR CODE BELOW ###

Q4 <- names(usairports)[1:6]

### VIEW OUTPUT ###
Q4

```

### Q5: Store the number of columns (i.e., the number of variables) in the usairports dataframe to Q5.

Do not hard code the answer! That is, do not simply have *`Q5 <- {a number}`*

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q5 #

### TYPE YOUR CODE BELOW ###

Q5 <- ncol(usairports)

### VIEW OUTPUT ###
Q5

```

### Q6: Use indexing to store the 3rd column name in the usairports data set to Q6.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q6 #

### TYPE YOUR CODE BELOW ###

Q6 <- names(usairports)[3]

### VIEW OUTPUT ###
Q6

```

### Q7: Store the values of the first 6 values of the `ownership` variable in the usairports dataframe to Q7. Use the `$` operator to access the values.

For assistance with the `$` operator, see this [article](https://statisticsglobe.com/meaning-of-dollar-operator-in-r)

Or, refer to the article ["How to Access Components of a Dataframe"](https://www.datamentor.io/r-programming/data-frame/)

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q7 #

### TYPE YOUR CODE BELOW ###

Q7 <- usairports$ownership[1:6]

### VIEW OUTPUT ###
Q7

```

### Q8: Use the length function to store the number of rows of the ownership variable in the usairports data set. Store the value in Q8.

Do not hard code the answer! That is, do not simply have `Q8 <- {a number}`

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q8 #

### TYPE YOUR CODE BELOW ###

Q8 <- length(usairports$ownership)

### VIEW OUTPUT ###
Q8

```

### Q9: Store the values of the ownership variable in a table and assign the table to Q9.

Read this [documentation](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/table) for assistance.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q9 #

### TYPE YOUR CODE BELOW ###

Q9 <- table(usairports$ownership)

### VIEW OUTPUT ###
Q9

```

------------------------------------------------------------------------

## Part 2

### Q10: Create a vector with these names: Matthew, Mark, Luke, and John. Assign it to Q10.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q10 #

### TYPE YOUR CODE BELOW ###

Q10 <- c('Matthew', 'Mark', 'Luke', 'John')

### VIEW OUTPUT ###
Q10

```

### Q11: Create a vector with these valuees: 28, 16, 24, 21. Assign it to Q11.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q11 #

### TYPE YOUR CODE BELOW ###

Q11 <- c(28, 16, 24, 21)

### VIEW OUTPUT ###
Q11

```

### Q12: Create a vector with these values: 1071, 678, 1151, 879. Assign it to Q12.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q12 #

### TYPE YOUR CODE BELOW ###

Q12 <- c(1071, 678, 1151, 879)

### VIEW OUTPUT ###
Q12

```

### Q13: Create a vector with these names: tax collector, young man, physician, beloved. Assign it to Q13.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q13 #

### TYPE YOUR CODE BELOW ###

Q13 <- c('tax collector', 'young man', 'physician', 'beloved')

### VIEW OUTPUT ###
Q13

```

### Q14: Create a dataframe with Q10, Q11, Q12, and Q13. Assign it to Q14.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q14 #

### TYPE YOUR CODE BELOW ###

Q14 <- data.frame(Q10, Q11, Q12, Q13)

### VIEW OUTPUT ###
Q14

```

### Q15: Find the class of Q14. Assign it to Q15.

```{r}
### Do not change and do not delete the comment below. It is required for CodeGrade to run properly.
# CG Q15 #

### TYPE YOUR CODE BELOW ###

Q15 <- class(Q14)

### VIEW OUTPUT ###
Q15

```
